



\documentclass[11pt,a4paper]{report}
\usepackage{arabtex}
\usepackage[utf8]{inputenc}
%\usepackage[LFE,LAE]{fontenc}
\usepackage[arabic,english]{babel}

\begin{document}
%	\maketitle



Dear Mr.nicolas padoy,

I am writing to apply for the Phd position advertised in the 
Research Group CAMMA website. As requested, I enclose my cv and diplomas.
The subject matter is very appealing to me, and I believe that my strong
technical experience and education make me a highly competitive candidate
for this position. Besides computer vision (artificial vision) is one of my favorite topic due to the multiple areas of application, making human life much easier and sometimes saving their lives.


I have successfully designed, developed and supported live-use applica-
tions during my master formation.
I strive continually for excellence and i learned a lot about computer vision
and how to manipulate, extract informations from images.
I have a great ambition to be part of the research field specially in Artificial intelligence ( computer vision) because i want to use  my knownledge and skills (hard and soft skills) in order to solve this subject matter by making the real-world AI-based solutions coming to life.


With a Master degree in Computer science (Artificial intelligence), I have
a comprehensive understanding of the full lifecycle for software development
projects and i master plenty of tools in order to optimize tasks in programs.
Please see my resume for additional information on my experience.
Thank you for your time and consideration. I look forward to speaking

with you about this employment opportunity.

Sincerely,


Moulai Hassina Safaa.
\end{document}

